\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Danil Sidorov} \\ \vspace{1pt}
  \small 732-856-4305 $|$ \href{mailto:danilsidorov8625@gmail.com}{\underline{danilsidorov8625@gmail.com}} $|$ 
  \href{https://linkedin.com/in/danil-sidorov-844109217/}{\underline{linkedin.com/in/danil-sidorov-844109217}} $|$
  \href{https://github.com/DanilSidorov8625}{\underline{github.com/DanilSidorov8625}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Pennsylvania State University}{State College, PA}
    {B.S. in Computer Science, GPA: 3.89}{Aug 2021 -- May 2025}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Full Stack Software Developer (Freelance)}{July 2022 -- Present}
    {PEX}{Remote}
    \resumeItemListStart
      \resumeItem{Engineered and maintained a cross-platform logistics application using React Native, serving over 5,000 monthly users by integrating with a legacy PHP backend via a modular API layer.}
      \resumeItem{Developed key features including a barcode scanning system that reduced manual data entry errors by 95\%, role-based access control (RBAC), and automated CSV/email exports.}
      \resumeItem{Implemented a RAG-based AI support chatbot using vector search, which successfully automated responses for 30\% of common customer inquiries and provided Russian localization (i18n).}
    \resumeItemListEnd

  \resumeSubheading
    {Network Engineer}{June 2025 -- Present}
    {Verizon}{Basking Ridge, NJ}
    \resumeItemListStart
      \resumeItem{Collaborated with stakeholders to define requirements and technical specifications for internal software enhancements, translating business needs into actionable development tasks.}
      \resumeItem{Analyzed backend APIs, frontend UI, and data workflows to identify bottlenecks, contributing to a 15\% improvement in overall ticket resolution times for critical internal applications.}
    \resumeItemListEnd

  \resumeSubheading
    {Computer Science Intern (2 summers)}{Summers 2022 \& 2023}
    {Verizon}{Basking Ridge, NJ}
    \resumeItemListStart
      \resumeItem{Built dashboards using Splunk, Tableau, and Python, improving customer order problem resolution by 26\% (from 27 to 20 days).}
      \resumeItem{Developed an ML model to classify ticket types with 92\% accuracy, decreasing average ticket resolution time by 17\%.}
    \resumeItemListEnd

  \resumeSubheading
    {Private eBay Seller}{2019 -- 2023}
    {Self-employed}{Remote}
    \resumeItemListStart
      \resumeItem{Operated a private eBay store, managing product sourcing, multi-party negotiations, and international logistics for technology and collectible items.}
      \resumeItem{Achieved \$145K in gross revenue over four years through strategic pricing and market analysis.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{One Million Images} $|$ \emph{Vanilla JS, Node.js, Socket.io, Redis, SQLite, R2}}{2024}
    \resumeItemListStart
        \resumeItem{Developed a massively multiplayer web application featuring a 1000x1000 grid where users can permanently upload images to a shared, zoomable canvas.}
        \resumeItem{Engineered a custom tile-based rendering system to efficiently display portions of the grid, ensuring smooth panning and zooming with minimal client-side resource usage.}
        \resumeItem{Utilized Socket.io for real-time grid updates, Redis for high-speed caching of image metadata, and Cloudflare R2 for low-cost, high-availability object storage.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, C, JavaScript, SQL, HTML/CSS} \\
    \textbf{Frameworks}{: React Native, Node.js, Flask, Next.js, Express, Tailwind, Deno} \\
    \textbf{Developer Tools}{: Git, Docker, Google Cloud, Firebase, VS Code, Splunk, Tableau} \\
    \textbf{Databases}{: SQLite, PostgreSQL, Redis} \\
    \textbf{Libraries}{: Redux, Chart.js, Sentry, Jest}
  }}
\end{itemize}

%-----------AWARDS-----------
\section{Awards}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{Dean's List (every semester), Penn State Discover Award (\$4,000/year), Penn State Commonwealth Award (\$2,000/year), Verizon (Recognizing You) Performance Award (\$500)}}
\end{itemize}

\end{document}